Results publications are inadequately linked to trial registrations: An automated pipeline and evaluation of German university medical centers

### 2021-09-06 docs/manuscript/manuscript.Rmd
Update appendix format to supplemental material

The IntoValue dataset includes all trials conducted by a German UMC that were registered on ClinicalTrials.gov or DRKS and completed between 2009 and 2017 (n = `r n_trials_iv`). After applying our exclusion criteria, our sample included `r n_trials_ft` trials with `r n_pubs_unique` unique results publications indexed in PubMed and available as full-text, as some publications include results from more than one trial. Appendix \@ref(app-flow-trials) provides a flow diagram of the trial and publication screening. Table \@ref(tab:tbl-trials) shows summary descriptive details of the trials with results publications by registry.

@@

Across the adjusted multivariate models,<!--#in the adjusted analysis,--> trials with one link type were generally more likely to have another type of link. <!--#However, trials with a TRN in the full-text were significantly less likely to have the publication linked in the registration (`r inline_text(aor_reg, variable = "has_iv_trn_ft", pattern = "aOR {estimate} [{ci}]")` ; `r inline_text(aor_ft, variable = "has_reg_pub_link", pattern = "aOR {estimate} [{ci}]")`).--> In particular, TRNs were more likely to appear in the PubMed metadata if included in the abstract (`r inline_text(aor_si, variable = "has_iv_trn_abstract", pattern = "aOR {estimate} [{ci}]")`), but not more likely if included in the full-text (`r inline_text(aor_si, variable = "has_iv_trn_ft", pattern = "aOR {estimate} [{ci}]")`). DRKS TRNs were less likely than ClinicalTrials.gov TRNs to appear in the PubMed metadata (`r inline_text(aor_si, variable = "registry", level = "DRKS", pattern = "aOR {estimate} [{ci}]")`). Similarly, for trials with a TRN in either abstract or full-text, ClinicalTrials.gov TRNs appeared at a higher rate than DRKS TRNs in the metadata (`r inline_text(tbl_si_abs_or_ft, "has_iv_trn_secondary_id", column = "stat_1", pattern = "{p}%")` vs. `r inline_text(tbl_si_abs_or_ft, "has_iv_trn_secondary_id", column = "stat_2", pattern = "{p}%")`). Appendix \@ref(app-si-if-abs-ft) shows the number and proportion of trials with a TRN in the metadata given a TRN in the abstract, full-text, or either, both overall and by registry.

>>>>

The IntoValue dataset includes all trials conducted by a German UMC that were registered on ClinicalTrials.gov or DRKS and completed between 2009 and 2017 (n = `r n_trials_iv`). After applying our exclusion criteria, our sample included `r n_trials_ft` trials with `r n_pubs_unique` unique results publications indexed in PubMed and available as full-text, as some publications include results from more than one trial. Supplemental Figure \@ref(fig:app-fig-flow-trials) provides a flow diagram of the trial and publication screening. Table \@ref(tab:tbl-trials) shows summary descriptive details of the trials with results publications by registry.

@@

Across the adjusted multivariate models,<!--#in the adjusted analysis,--> trials with one link type were generally more likely to have another type of link. <!--#However, trials with a TRN in the full-text were significantly less likely to have the publication linked in the registration (`r inline_text(aor_reg, variable = "has_iv_trn_ft", pattern = "aOR {estimate} [{ci}]")` ; `r inline_text(aor_ft, variable = "has_reg_pub_link", pattern = "aOR {estimate} [{ci}]")`).--> In particular, TRNs were more likely to appear in the PubMed metadata if included in the abstract (`r inline_text(aor_si, variable = "has_iv_trn_abstract", pattern = "aOR {estimate} [{ci}]")`), but not more likely if included in the full-text (`r inline_text(aor_si, variable = "has_iv_trn_ft", pattern = "aOR {estimate} [{ci}]")`). DRKS TRNs were less likely than ClinicalTrials.gov TRNs to appear in the PubMed metadata (`r inline_text(aor_si, variable = "registry", level = "DRKS", pattern = "aOR {estimate} [{ci}]")`). Similarly, for trials with a TRN in either abstract or full-text, ClinicalTrials.gov TRNs appeared at a higher rate than DRKS TRNs in the metadata (`r inline_text(tbl_si_abs_or_ft, "has_iv_trn_secondary_id", column = "stat_1", pattern = "{p}%")` vs. `r inline_text(tbl_si_abs_or_ft, "has_iv_trn_secondary_id", column = "stat_2", pattern = "{p}%")`). Supplemental Table \@ref(tab:app-tbl-si-if-abs-ft) shows the number and proportion of trials with a TRN in the metadata given a TRN in the abstract, full-text, or either, both overall and by registry.
